%-------------------------
% Aadith Thiruvangadan Resume - LaTeX Code
% Clean, Recruiter-Friendly, ATS-Optimized Template
% Suitable for compilation in Overleaf (pdflatex)
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%-------------------------
% PAGE SETUP
%-------------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\cleanlook

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% CUSTOM COMMANDS
%-------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Aadith Thiruvangadan} \\ \vspace{8pt}
    \small Kannur, Kerala, India $|$ \href{mailto:aadiththiruvangadan@gmail.com}{aadiththiruvangadan@gmail.com} $|$ +91-9744345247 \\
    \small \href{https://linkedin.com/in/aadiththiruvangadan}{linkedin.com/in/aadiththiruvangadan} $|$ \href{https://github.com/aadiththiruvangadan}{github.com/aadiththiruvangadan}
\end{center}


%-----------SUMMARY-----------
\section{Professional Summary}
Motivated Software Developer with skills in Python, SQL, and web development, passionate about building efficient software solutions and continuously learning new technologies. Strong problem-solving abilities with a focus on delivering quality results.


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:}{ Python, C, SQL} \\
     \textbf{Core Concepts:}{ Object-Oriented Programming (OOP), Data Structures, Algorithms} \\
     \textbf{Web Development:}{ HTML, CSS, JavaScript, PHP} \\
     \textbf{Frameworks/Databases:}{ Django, MySQL, Oracle SQL} \\
     \textbf{Data Science \& ML:}{ Scikit-learn, XGBoost, Pandas, NumPy, OpenCV} \\
     \textbf{Tools:}{ Git, GitHub, Power BI, Excel, VS Code}
    }}
\end{itemize}


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading{YouTube Video Views Prediction using Machine Learning}{}{}{}
    \vspace{-15pt}
    \small{\textit{Technologies: Python, Scikit-learn, XGBoost, Pandas, NumPy}}
    \resumeItemListStart
      \resumeItem{Built ML model to predict video views using title and likes.}
      \resumeItem{Performed data preprocessing, feature engineering, and text handling for title-based inputs.}
      \resumeItem{Applied TF-IDF and feature engineering to convert raw text titles into numerical weights.}
      \resumeItem{Implemented an XGBoost regression model achieving strong prediction performance (81\% accuracy).}
    \resumeItemListEnd

    \resumeSubheading{Detecting Humans in Search and Rescue}{}{}{}
    \vspace{-15pt}
    \small{\textit{Technologies: Python, YOLO, OpenCV, Django, HTML, CSS, JavaScript}}
    \resumeItemListStart
      \resumeItem{Implemented real-time human detection using YOLO and OpenCV on live video streams for search-and-rescue applications.}
      \resumeItem{Optimized model performance parameters, threshold filters, and frame scaling for faster and accurate detection.}
    \resumeItemListEnd

    \resumeSubheading{Payroll Management System}{}{}{}
    \vspace{-15pt}
    \small{\textit{Technologies: HTML, CSS, JavaScript, PHP, MySQL}}
    \resumeItemListStart
      \resumeItem{Developed a web-based application to automate salary processing and tax calculations.}
      \resumeItem{Implemented secure employee self-service features restricting access to authorized records.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------TRAINING-----------
\section{Training}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Python Fullstack and Data Science Training}{July 2025 -- March 2026}
      {Pyspiders / Qspiders}{Kannur, India}
      \resumeItemListStart
        \resumeItem{Training in Python Full Stack Development covering Core Python, Object-Oriented Programming (OOP), Django, REST APIs, HTML, CSS, JavaScript, Power BI, SQL, NumPy, Pandas, Statistics, and Machine Learning concepts.}
        \resumeItem{Built foundational knowledge in full-stack development and data analysis.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {College Of Engineering Trikaripur}{Nov 2021 -- Apr 2025}
      {B.Tech in Computer Science}{Trikaripur, India}
    \resumeSubheading
      {Govt HSS Kannadiparamba}{Jun 2019 -- Mar 2021}
      {Higher Secondary Education (HSC)}{Kannur, India}
  \resumeSubHeadingListEnd


%-----------CERTIFICATES-----------
\section{Certificates}
  \resumeItemListStart
    \resumeItem{NPTEL : Joy of Computing Using Python (IIT Madras)}
    \resumeItem{Qspiders : Python Full Stack and Data Science}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
